Rusty Variation\\ Deadlock-free Sessions with Failure in Rust

### 2019-11-20 doc/ice2019/main.tex
Rebranded, deleted some slides.

We argue that even if Rust were able to enforce linearity, the \emph{idea} of linear session types is flawed (see~\cref{sec:cancellation}), as sessions may be dropped at any time, for any number of reasons, \eg a process panicking, dropping all sessions in scope.

The following two programs illustrate the difference in handling failure between Rusty Variation and the work by Laumann \etal~\cite{jespersen2015}. In both programs, the programmer has forgotten to complete the server, accidentally dropping the session endpoint \lstinline{_s} or channel \lstinline{_c}, respectively. The program on the left, written in RV, returns an error. The program on the right, written using the library described by Laumann \etal\cite{jespersen2015}, segfaults. We have since reported this segfault to Laumann \etal, and they have fixed it in the most recent version of the library. The program on the right now panics:

>>>>

We argue that even if Rust were able to enforce linearity statically, the \emph{idea} of linear session types is flawed (see~\cref{sec:cancellation}), as sessions may be dropped at any time, for any number of reasons, \eg a process panicking, dropping all sessions in scope.

The following two programs illustrate the difference in handling failure between Rusty Variation and the work by Laumann \etal~\cite{jespersen2015}. In both programs, the programmer has forgotten to complete the server, accidentally dropping the session endpoint \lstinline{_s} or channel \lstinline{_c}, respectively. The program on the left, written in RV, returns \lstinline{None}. The program on the right, written using the library described by Laumann \etal\cite{jespersen2015}, segfaults. We have since reported this segfault to Laumann \etal, and they have fixed it in the most recent version of the library. The program on the right now panics:
